---
title: "My R Markdown Document"
output: html_document
spellcheck: false
---

# Task: Polynomial Regression Analysis in R

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

Perform a polynomial regression analysis using the mtcars dataset in R. The database contains information on different car models, including horsepower (hp) and miles per gallon (mpg) performance.

**1. Fit a simple linear regression model**.

Complete the code to fit a simple linear regression model. Use the lm() function to fit the model.

```{r task1}
# TODO

```

**2. Create the scatter plot with the regression line**.

Complete the code to create the scatter plot to show the relationship between the variables hp and mpg \# Use the plot() function to create the scatter plot. \# Use the abline() function to add the regression line to the graph.

```{r task2, echo=T}
# TODO
```

**3. Make predictions with the simple linear model**

Complete the code to make predictions for new horsepower (hp) quantities

Create a new dataframe with the new hp quantities using the data.frame() function.

Use the predict() function to make predictions using the model fitted in task 1.

```{r task3, echo=FALSE}
# TODO

```

**4. Fit a cubic regression model**.

Complete the code to fit a cubic regression model

Use the lm() function to fit the cubic model.

Note that to include polynomial terms, the \^ function must be used to raise the variables.

```{r task4, echo=FALSE}
# TODO

```

**5. Create the scatter plot with the cubic regression curve**.

Complete the code to create the scatter plot showing the relationship between hp and mpg

Use the plot() function to create the scatter plot.

Use the lines() function to add the cubic regression curve to the graph.

```{r task5, echo=FALSE}
# TODO

```

**6. Analyze and compare the results of both regression models**.

Complete the code to analyze and compare the results of both regression models. Discuss the suitability of each model to represent the relationship between the variables.

```{r task6, echo=FALSE}
# TODO

```

Additional instructions: - Be sure to include appropriate titles, labels, and colors on graphs for better visual representation. - Provide clear and detailed explanations in the code comments to facilitate the understanding of the analysis performed.
